
\documentclass[10pt,a4paper]{altacv}
\geometry{left=1.3cm,right=1.3cm,top=1.2cm,bottom=1.2cm,columnsep=1.2cm}
\usepackage{paracol}
\usepackage{fontawesome5}

\name{Anaha Joy}
\tagline{Data Engineer : Web Data Scraping Intern with Full Time opportunity}
\personalinfo{%
  \email{anahajoy2022@gmail.com}
  \phone{+91 8304078233}
  \location{India, Thodupuzha}
}

\begin{document}
\makecvheader

% ===== SUMMARY =====
\cvsection{Summary}
\begin{quote}
Here is a rewritten professional summary for Anaha Joy:

Results-driven Data Engineer with 2+ years of experience in designing, developing, and optimizing scalable data solutions, leveraging expertise in Python, SQL, and data integration tools. Proven track record of driving efficiency and ensuring data quality through ETL pipeline development, data modeling, and data transformation projects. Skilled in facilitating data-driven decision-making and supporting business intelligence initiatives, with a strong foundation in data engineering principles and technologies.
\end{quote}

% ===== SKILLS =====
\cvsection{Skills}
\cvtag{Technicalskills}: ETL Development & Data Integration, Data Modeling & Warehousing, Data Visualization & Reporting, Data Quality & Testing, Business Intelligence & Analytics, Web Data Scraping, Data Transformation, Data Warehousing, Data Validation \\ 
\cvtag{Tools}: SSIS, DBT, Power Query, Jinja, Power BI, Tableau, Power BI Report Builder, Paginated Reports, Scrapy, BeautifulSoup, Puppeteer/Playwright, Redis, Elasticsearch \\ 
\cvtag{Cloudskills}: Azure Data Factory (ADF), Azure, Azure Storage, Azure DevOps \\ 
\cvtag{Languages}: Python, JavaScript, SQL, HTML, CSS \\ 

\cvsection{Experience}

\cvevent{Data and AI Engineer}{Experion Technologies}{2024 - present}{}
\begin{itemize}
  \item Developed scalable data pipelines using Azure Data Factory, leveraging skills in data processing and optimization to inform web scraping pipeline development.
  \item Utilized SQL and data modeling expertise to design efficient data storage solutions, ensuring data accuracy and reliability in large datasets.
  \item Collaborated with cross-functional teams to integrate data solutions, demonstrating ability to work with engineering and data teams to integrate scraped data into downstream systems.
\end{itemize}

\cvevent{Associate Data Engineer}{Experion Technologies}{2023-2024}{}
\begin{itemize}
  \item Applied data transformation expertise using SQL and Power Query to optimize data processing, relevant to optimizing scrapers for efficiency and reliability.
  \item Managed data integrity through Snowflake validation and query optimization, ensuring data accuracy and validation in large datasets.
  \item Developed actionable data solutions, demonstrating ability to explore and implement latest tools and techniques, such as Scrapy, BeautifulSoup, and Puppeteer/Playwright.
\end{itemize}

\cvsection{Education}

\cvevent{MBA with Data Science}{Amity University}{2025 - Present}{GPA: }

\cvevent{Bachelor of Computer Application}{Mahathma Ghandi University}{2019-2022}{GPA: 8.05}

\cvsection{Certifications}
\cvachievement{\faCertificate}{Database Management System}{IIT Madras}{}
\cvachievement{\faCertificate}{Google Analytics Certification}{Google}{}
\cvachievement{\faCertificate}{Cloud Computing}{IIT Kharagpur}{}

\cvsection{Achievements}
\cvachievement{\faTrophy}{Led feedback analysis for a smart technology platform supporting a U.S.-based client.}{}{}
\cvachievement{\faTrophy}{Delivered actionable business intelligence, guiding client workflow improvements and strategic decisions.}{}{}
\cvachievement{\faTrophy}{Received positive client testimonials and recognition for collaborative approach, analytical precision, and client-focused solutions.}{}{}

\end{document}